### 2020-03-18 README.Rmd
Revert "working on fit_bayesian_model"
This reverts commit f0113776f76d6185b3d0fe029c93ab64062e6231.
Done spatial residuals plot

```{r}
focal_vs_comp_bw <- bw_growth_df %>% 
  create_focal_vs_comp(max_dist = max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
```

@@

```{r}
bw_predict <- focal_vs_comp_bw %>% 
  predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model)

# TODO: Convert output of predict_bayesian_model() to be of focal_vs_focal type
# TODO: Preserve geometry variable, that way we can easily create residual plots

bw_predict %>%
  group_by(focal_ID, focal_notion_of_species) %>%
  # Since for the same focal tree all growth & growth_hat values are the same:
  summarise(growth = mean(growth), growth_hat = mean(growth_hat)) %>%
  ggplot(aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0,0,0,0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh", 
    title = "Predicted vs Observed Growth"
  )
```

>>>>

```{r}
focal_vs_comp_bw <- bw_growth_df %>% 
  create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
```

@@

```{r}
bw_growth_df <- focal_vs_comp_bw %>% 
  predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model) %>% 
  right_join(bw_growth_df, by = c("focal_ID" = "treeID"))

bw_growth_df <- bw_growth_df %>% 
  st_as_sf()

# Observed vs predicted growth  
ggplot(bw_growth_df, aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0, 0, 0, 0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh", 
    title = "Predicted vs Observed Growth"
  )

reslab <- expression(paste('Residual (cm ',y^{-1},')'))
bw_growth_df %>% 
  # Need to investigate missingness
  filter(!is.na(growth_hat)) %>% 
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5), 
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>% 
  ggplot() + 
  geom_sf(aes(col = error_compress), size = 0.4) + 
  theme_bw() + 
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf", 
    name = reslab,
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c('< -0.75', '-0.5', '0.25', '0', '0.25', '0.5', '> 0.75')) +
  labs(x = "Meter", y = "Meter")
```
